{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

    \subsection{A compact argument for the convergence of NAPG with proximal gradient}
        Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
        It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
        The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
        It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
        \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
            Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
            Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
            Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
            Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
                & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right). 
            If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
                F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
            The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
            For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
                \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
                \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
                \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
                \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}. 
                \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
                \item [(f)] Using basic algebra, we have the following equality: 
                    (\forall k \ge 1)\; \frac{1}{2}\left(
                        \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
                    \right) &= 
                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
                \item [(g)] Using (c), we have the following equality: 
                    \frac{1}{2}\left(
                        \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
                        \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
                    \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
                \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
                    (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
            With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
            The overall proof now follows. 
            Start with the (a), the proximal gradient inequality it has: 
                0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
                    - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                    - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
            Using the chain of equality below: 
            {\footnotesize
                &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
                -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
                    &\quad +
                    \frac{L_k - \mu}{2}
                        \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
                        \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
                - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
                    + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                &= \left(
                    \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
                    \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
                    - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
                \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                &\underset{\text{(g)}}{=}
                \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
                \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
                    \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
                        \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
                &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
            The inequality from previously simplifies, and it has: 
            {\allowdisplaybreaks\small
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
                    + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
                &\underset{\text{(h)}}{\le}
                \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
                    + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\ &\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                    F(x_{k - 1}) - F(\bar x) 
                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                &\le (1 - \alpha_k)\left(
                    \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
                    + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
                    \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad 
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
                    F(x_{k - 1}) - F(\bar x) 
                    + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                \right) \\&\quad
                    + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
            Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
                0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
                &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
            Going back to prove the intermediate results, the following will be useful. 
            From Definition \ref{def:st-method} it has for all $k \ge 0$
            \begin{align}\label{thm:onestep-napg-cnvg-i}
                \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
            \tag{i}\end{align}
            Then it has: 
            \begin{align*}\label{thm:onestep-napg-cnvg-j}
                &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
                    1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                    \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
            \tag{j}\end{align*}
            And also
            \begin{align*}\label{thm:onestep-napg-cnvg-k}
                \tau_k(1 + \tau_k)^{-1} 
                &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
                \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
                \frac{L_k\alpha_k - \mu}{L_k - \mu}
                = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
            \tag{k}\end{align*}
            \textbf{Proof of (d)}
            For all $k \ge 1$, from Definition \ref{def:st-method} it has 
                &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
                (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
                        \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
                    + (1 - \alpha_k)\left(
                        \frac{L_k}{L_k - \mu} - 1
                &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
                \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
                \iff 
                (1 - \alpha_k)x_{k - 1} - y_k 
                &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
            Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
                z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
                &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
                \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
                - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                    \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
                \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
                \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
                &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
                \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
            The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 

>>>>

    % \subsection{A compact argument for the convergence of NAPG with proximal gradient}
    %     Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
    %     It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
    %     The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
    %     It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
    %     \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
    %         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
    %         Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
    %         Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
    %         Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
    %         \begin{align*}
    %             & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right). 
    %         \end{align*}
    %         If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
    %         \begin{align*}
    %             F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
    %             &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
    %         \end{align*}
    %     \end{theorem}
    %     \begin{proof}
    %         The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
    %         \par
    %         For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
    %         \begin{itemize}
    %             \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
    %             \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
    %             \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
    %             \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}. 
    %             \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
    %             \item [(f)] Using basic algebra, we have the following equality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; \frac{1}{2}\left(
    %                     \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
    %                 \right) &= 
    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
    %             \end{align*}
    %             \item [(g)] Using (c), we have the following equality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; 
    %                 \frac{1}{2}\left(
    %                     \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
    %                     \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
    %                 \right)
    %                 &= 
    %                 \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
    %             \end{align*}
    %             \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
    %             \end{align*}
    %         \end{itemize}
    %         With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
    %         The overall proof now follows. 
    %         Start with the (a), the proximal gradient inequality it has: 
    %         \begin{align*}
    %             0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
    %             \\
    %             &\underset{\text{(b)}}{\le}
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
    %                 &\quad 
    %                 - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
    %         \end{align*}
    %         Using the chain of equality below: 
    %         {\footnotesize
    %         \begin{align*}
    %             &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %             + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
    %             \\
    %             &\underset{\text{(d)}}{=} 
    %             -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
    %                 &\quad +
    %                 \frac{L_k - \mu}{2}
    %                 \left\Vert 
    %                     \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
    %                     \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
    %                 \right\Vert^2
    %             \\
    %             &= 
    %             - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
    %                 + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &= \left(
    %                 \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \left(
    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &\underset{\text{(f)}}{=} 
    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \left(
    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &\underset{\text{(g)}}{=}
    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
    %             \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
    %                     \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
    %                 \right)
    %             \\
    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
    %         \end{align*}
    %         }
    %         The inequality from previously simplifies, and it has: 
    %         {\allowdisplaybreaks\small
    %         \begin{align*}
    %             0 &\le 
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
    %             + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
    %                 + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
    %             \\
    %             &\underset{\text{(h)}}{\le}
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
    %                 \\ &\quad
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %             \\
    %             &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %             \\
    %             &\underset{\text{(e)}}{=} 
    %             (1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\ &\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &\le 
    %             (1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &\le (1 - \alpha_k)\left(
    %                 \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad 
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &= 
    %             \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
    %         \end{align*}
    %         }
    %         Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
    %         \begin{align*}
    %             0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
    %             \\
    %             &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
    %         \end{align*}

    %         \par
    %         Going back to prove the intermediate results, the following will be useful. 
    %         From Definition \ref{def:st-method} it has for all $k \ge 0$
    %         \begin{align}\label{thm:onestep-napg-cnvg-i}
    %             \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
    %         \tag{i}\end{align}
    %         Then it has: 
    %         \begin{align*}\label{thm:onestep-napg-cnvg-j}
    %             (1 + \tau_k)^{-1}
    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
    %             \left(
    %                 1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \right)^{-1} = \left(
    %                 \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \right)^{-1}
    %             = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
    %         \tag{j}\end{align*}
    %         And also
    %         \begin{align*}\label{thm:onestep-napg-cnvg-k}
    %             \tau_k(1 + \tau_k)^{-1} 
    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
    %             \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}
    %             = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
    %         \tag{k}\end{align*}
    %         \textbf{Proof of (d)}
    %         For all $k \ge 1$, from Definition \ref{def:st-method} it has 
    %         \begin{align*}
    %             0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
    %             \\
